Epwshiftr: incorporating open data of climate change prediction into \vspace{4pt} building performance simulation for future adaptation and mitigation\\

### 2024-01-03 full-paper/paper.tex
paper: rebuild tex and zip

A rich body of research and development exists on weather generators for
creating future weather data for BES. In 2005, \citet{belcher2005constructing} proposed
the morphing method, a relatively simple statistical downscaling
method. It is based on the future climate change data predicted by the Global
Climate Model (GCM) and hourly weather data, usually a typical meteorological
year (TMY). Morphing can capture the average future weather conditions from GCM
while preserving historical weather sequences. It requires low computational
power, making it possible to create many weather files from worldwide locations.
However, morphing may under- or overestimate climate change impacts because of
the lacking of ability to capture future extreme weather conditions and
potential differences in the reference time frame of the TMY and GCM data
\citep{moazami2019impacts}.
Moreover, careful consideration should be given to morphing when modifying
individual meteorological variables independently, breaking their physical
relationships. Despite these shortcomings, this method is still widely used
because of its simple and flexible characteristics.
Multiple morphing-based future weather
generators have been developed over the decades to integrate climate change
predictions from CMIP (Coupled Model Intercomparison Project) projects that
cover worldwide locations \citep{jentsch2008climate, troup2016morphing, dickinson2016generating, yassaghi2019overview}. Currently,
CCWorldWeatherGen\citep{jentsch2013transforming}, WeatherShift
\citep{dickinson2016generating}, and Meteonorm \citep{remund2020meteonorm} are three
future weather generators widely used in literature. CCWorldWeatherGen provides
a graphical interface based on Microsoft Excel to generate weather files in EPW
format supported by EnergyPlus directly. However, it is based on the A2 climate
scenario from the IPCC Third Assessment Report (TAR) published in 2001. Moreover,
it only utilizes data from a single GCM called HadCM3. Like CCWorldWeatherGen,
WeatherShift and Meteonorm also use morphing to generate EPW files for future
climate. They consider two representative concentration pathway (RCP) emission
scenarios, i.e., RCP4.5 and RCP8.5, from the 2014 IPCC Fifth Climate Change
Assessment Report (AR5). At the same time, both are commercial products, and the
weather data under a single climate scenario often cost hundreds of dollars.

@@

Since each NetCDF file contains data of a complete global grid, the size of the
monthly global surface temperature forecast data for the next 20 years under a
single climate scenario can reach more than 1 GB. The CMIP6 ScenarioMIP contains
dozens of different GCMs, and the total size of all output files will get more
than 10 TB, making it impossible to download all of them for analysis.

The \emph{Query Module} provides an interface utilizing the RESTful API provided by
ESGF. It thus is capable of querying all CMIP6 GCM outputs based on various
conditions, providing download links of NetCDF files. The query result will be
processed into a data frame that contains 22 metadata that describes each
output. Also, an output index is generated based on the query to
check the data integrity before extracting climate change data.

@@

\begin{itemize}
\tightlist
\item
  Warnings are generated if there are any missing values in the input EPW and
  GCM data.
\item
  Unit conversions between data of EPW and GCM are automatically performed using
  the units \citep{pebesma2016measurement} R package, e.g.~all temperature data have
  been converted to Celsius before calculation.
\item
  Calculation of dew point temperature is performed based on dry-bulb
  temperature and relative humidity using the psychrolib \citep{meyer2019psychrolib}
  R package.
\item
  Input values of relative humidity that exceed 100\% will be reset to 100\%.
\item
  A threshold value is set for the stretch factor (\(\alpha\)), i.e.~monthly-mean
  fractional change, when performing morphing operations. The default value is
  set to \texttt{3}. If the absolute \(\alpha\) exceeds this threshold value, warnings
  are issued to suggest users further investigate the input data before
  continuing. Moreover, the morphing method will use the shift factor (\(\Delta x\))
  to to avoid unrealistic morphed values.
\end{itemize}

@@

Currently, epwshiftr only supports the morphing method. But the \texttt{morphing\_epw}
interface provides parameters to modify which factors should be used for each
meteorological variable, with meaningful defaults value given. For example,
radiation-related variables are, by default, morphed using the stretch factor,
avoiding unrealistic positive values at nighttime. The modular design pattern of
epwshiftr makes it decouple the data structure and the actual extrapolation
algorithm used. We are happy to explore the feasibility of supporting
alternative extrapolation algorithms in the future.

@@

This study was funded by Research Foundation of Chongqing University of Science
and Technology (project No.~ckrc2021073) and the 111 project (Grant No.~B13041),
The authors also thank the support from the Berkeley Education Alliance for
Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
Sustainability in the Tropics (SinBerBEST) Program.

>>>>

A rich body of research and development exists on weather generators for
creating future weather data for BES. In 2005, \citet{belcher2005constructing} proposed
the morphing method, a relatively simple statistical downscaling
method. It is based on the future climate change data predicted by the Global
Climate Model (GCM) and hourly weather data, usually a typical meteorological
year (TMY). Morphing can capture the average future weather conditions from GCM
while preserving historical weather sequences. It requires low computational
power, making it possible to create many weather files from worldwide locations.
However, morphing may under- or overestimate climate change impacts because of
the lack of ability to capture future extreme weather conditions and
potential differences in the reference time frame of the TMY and GCM data
\citep{moazami2019impacts}.
Moreover, careful consideration should be given to morphing when modifying
individual meteorological variables independently, breaking their physical
relationships. Despite these shortcomings, this method is still widely used
because of its simple and flexible characteristics.
Multiple morphing-based future weather
generators have been developed over the decades to integrate climate change
predictions from CMIP (Coupled Model Intercomparison Project) projects that
cover worldwide locations \citep{jentsch2008climate, troup2016morphing, dickinson2016generating, yassaghi2019overview}. Currently,
CCWorldWeatherGen\citep{jentsch2013transforming}, WeatherShift
\citep{dickinson2016generating}, and Meteonorm \citep{remund2020meteonorm} are three
future weather generators widely used in the literature. CCWorldWeatherGen provides
a graphical interface based on Microsoft Excel to generate weather files in EPW
format supported by EnergyPlus directly. However, it is based on the A2 climate
scenario from the IPCC Third Assessment Report (TAR) published in 2001. Moreover,
it only utilizes data from a single GCM called HadCM3. Like CCWorldWeatherGen,
WeatherShift and Meteonorm also use morphing to generate EPW files for future
climate. They consider two representative concentration pathway (RCP) emission
scenarios, i.e., RCP4.5 and RCP8.5, from the 2014 IPCC Fifth Climate Change
Assessment Report (AR5). At the same time, both are commercial products, and the
weather data under a single climate scenario often costs hundreds of dollars.

@@

Since each NetCDF file contains data of a complete global grid, the size of the
monthly global surface temperature forecast data for the next 20 years under a
single climate scenario can reach more than 1 GB. The CMIP6 ScenarioMIP contains
dozens of different GCMs, and the total size of all output files will be more
than 10 TB, making it impossible to download all of them for analysis.

The \emph{Query Module} provides an interface utilizing the RESTful API provided by
ESGF. It thus is capable of querying all CMIP6 GCM outputs based on various
conditions, providing download links of NetCDF files. The query result will be
processed into a data frame that contains 22 metadata describing each
output. Also, an output index is generated based on the query to
check the data integrity before extracting climate change data.

@@

\begin{itemize}
\tightlist
\item
  Warnings are generated if there are any missing values in the input EPW and
  GCM data.
\item
  Unit conversions between data of EPW and GCM are automatically performed using
  the units \citep{pebesma2016measurement} R package, e.g.~all temperature data have
  been converted to Celsius before calculation.
\item
  Calculation of dew point temperature is performed based on dry-bulb
  temperature and relative humidity using the psychrolib \citep{meyer2019psychrolib}
  R package.
\item
  Input values of relative humidity that exceed 100\% will be reset to 100\%.
\item
  A threshold value is set for the stretch factor (\(\alpha\)), i.e.~monthly-mean
  fractional change, when performing morphing operations. The default value is
  set to \texttt{3}. If the absolute \(\alpha\) exceeds this threshold value, warnings
  are issued to suggest users further investigate the input data before
  continuing. Moreover, the morphing method will use the shift factor (\(\Delta x\))
  to avoid unrealistic morphed values.
\end{itemize}

@@

Currently, epwshiftr only supports the morphing method. But the \texttt{morphing\_epw}
interface provides parameters to modify which factors should be used for each
meteorological variable, with meaningful default values given. For example,
radiation-related variables are, by default, morphed using the stretch factor,
avoiding unrealistic positive values at nighttime. The modular design pattern of
epwshiftr makes it decouple the data structure and the actual extrapolation
algorithm used. We are happy to explore the feasibility of supporting
alternative extrapolation algorithms in the future.

@@

This study was funded by the Research Foundation of Chongqing University of Science
and Technology (project No.~ckrc2021073) and the 111 project (Grant No.~B13041).
The authors also thank the support from the Berkeley Education Alliance for
Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
Sustainability in the Tropics (SinBerBEST) Program.
